### 2016-01-18 p00-ch00-intro/intro.tex
Add table of publications

The rapid increase of computational power added a new aspect added to create a triangle: object-oriented, actor model, and \emph{concurrency}.
Concurrency makes it harder to verify programs in terms of correctness of runtime behavior~\cite{Herlihy:1990:linear,johnsen:history,agha:predictive:safety}. 
Scheduling of object messages in threads of executions is one of main challenges.
In addition, in the presence of scheduling and thread interleaving, it is important that objects are able to protect their state from concurrent modifications for correctness properties.
In this thesis, we take advantage of a modelling language that aims to mix the three aspects in addition to the capabilities of formal semantics and verification.

@@

One core challenge is to combine ABS semantics (e.g. concurrency layer) in a
programming language.
\TODO{Elaborate the core contributions of this thesis}
Considering the mainstream programming languages
\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}}, Java~\cite{gosling2000java} is one of the most commonly-used.
Since Java 1.5 and the rise of the concurrency API in Java~\cite{jsr166}, substantial effort is spend by the community on how concurrency and distribution can be improved in Java, along the lines of the actor model, as provided by ABS.
However, not all the development on Java libraries and frameworks are based on a rigorous formal semantics. 
Therefore, this gives rise to issues and challenges in terms of correctness, semantic preservation, and reasoning.

@@

\TODO{Connect back to the problem statement paraph}

In this thesis, we focus on the concurrency layer of ABS.
We formalize a subset of Java language in regards with ABS\TODO{Check for the way around}.
We provide the operational semantics of the concurrency layer for scheduling of actors with an extension for deadlines and priorities. 
We deliver ABS concurrency as a Java API.
We utilize Java~8 and Java Concurrency API to preserve the semantics of ABS concurrency layer.
We sketch a general architecture on how ABS language can be modularly translated into different programming languages.
We present how this ABS API library can be used to translate ABS models into Java.

Table~\ref{tbl:thesis} summarizes the structure of the research and contributions in the chapters of this text:

@@

>>>>

The rapid increase of computational power added a new aspect to create a triangle: object-oriented, actor model, and \emph{concurrency}.
Concurrency makes it harder to verify programs in terms of correctness of runtime behavior~\cite{Herlihy:1990:linear,johnsen:history,agha:predictive:safety}. 
Scheduling of object messages in threads of executions is one of main challenges.
In addition, in the presence of scheduling and thread interleaving, it is important that objects are able to protect their state from concurrent modifications for correctness properties.

@@

One core challenge is to combine ABS semantics (e.g. concurrency layer) in a
programming language.
Considering the mainstream programming languages
\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}}, Java~\cite{gosling2000java} is one of the most commonly-used.
Since Java 1.5 and the rise of the concurrency API in Java~\cite{jsr166}, substantial effort is spend by the community on how concurrency and distribution can be improved in Java, along the lines of the actor model, as provided by ABS.
However, not all the development on Java libraries and frameworks are based on a rigorous formal semantics. 
Therefore, this gives rise to issues and challenges in terms of correctness, semantic preservation, and reasoning.

@@

Based on the problem statement and approach taken in this research, 
Table~\ref{tbl:thesis} summarizes the structure of this text:

@@

In addition, Table~\ref{tbl:papers} summarizes the conference and journal 
publications as a result of this research:

\begin{table}[h]
\centering
\begin{tabular}{p{7cm}p{5cm}p{1cm}}
\textsfb{Topic} & \textsfb{Proceedings / Journal} & \textsfb{Year}   
\\ \toprule
Programming and Deployment of Active Objects with Application-Level Scheduling & ACM SAC 2012, Pages 1883--1888 & 2012 
\\ \midrule
The Future of a Missed Deadline & COORD 2013, Pages 181--195 & 2013 
\\ \midrule
Monitoring Method Call Sequences using Annotations & Journal of Science of Computer Programming, 2014, Volume 94, Part 3, Pages 362--378 & 2014 
\\ \midrule
Programming with actors in Java~8 & ISoLA 2014, Pages 37--53 & 2014 
\\ \midrule
Formal verification of service level agreements through distributed monitoring & ESOCC 2015, Pages 125--140 & 2015
\\ \bottomrule
\end{tabular}
\caption{Actors At Work -- Conference and Journal Publications}
\label{tbl:papers}
\end{table}
